Rubin Observatory Pointing Algorithm and Survey Simulation

### 2025-02-07 ms.tex

>>>>

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_ToO_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_ToO_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_ToO_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of ToO observations \label{fig:tiers_ddf}}
\end{figure}

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_blob_long_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_blob_long_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_blob_long_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of initial hour long timescale observations \label{fig:tiers_ddf}}
\end{figure}

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_long_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_long_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_long_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of final hour long timescale observations \label{fig:tiers_ddf}}
\end{figure}

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_greedy_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_greedy_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_greedy_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of greedy observations \label{fig:tiers_ddf}}
\end{figure}

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_pair_33_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_pair_33_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_pair_33_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of 33 minute paired observations observations \label{fig:tiers_ddf}}
\end{figure}

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_pair_15_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_pair_15_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_pair_15_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of 15 minute paired observations observations \label{fig:tiers_ddf}}
\end{figure}

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_twilight_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_twilight_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_twilight_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of twilight observations for earth interior objects. \label{fig:tiers_ddf}}
\end{figure}
